---
title: "Model Performance Results"
author: 'Zachary Katz (UNI: zak2132)'
date: "2023-03-14"
output: pdf_document
---

# Data Import & Wrangling

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse)
```

```{r, cache = TRUE, message = FALSE, warning = FALSE}
# Import model results

# Linear model
setwd("~/Desktop/Scenarios 11 & 12/Linear")
linear_results = list.files(path = "~/Desktop/Scenarios 11 & 12/Linear",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time / 60 # time in minutes
  ) %>% 
  distinct() %>% 
  select(-dataset)

# Elastic net model
setwd("~/Desktop/Scenarios 11 & 12/Elastic Net")
elastic_net_results = list.files(path = "~/Desktop/Scenarios 11 & 12/Elastic Net",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# MARS model
setwd("~/Desktop/Scenarios 11 & 12/MARS")
mars_results = list.files(path = "~/Desktop/Scenarios 11 & 12/MARS",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# GAM1 model
setwd("~/Desktop/Scenarios 11 & 12/GAM1")
gam1_results = list.files(path = "~/Desktop/Scenarios 11 & 12/GAM1",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time * 60 # convert to hours
  ) %>% 
  distinct() %>% 
  select(-dataset)

# Quantile G-Computation model
setwd("~/Desktop/Scenarios 11 & 12/Quantile G-Computation")
qgcomp_results = list.files(path = "~/Desktop/Scenarios 11 & 12/Quantile G-Computation",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# Causal Forest model
setwd("~/Desktop/Scenarios 11 & 12/Causal Forest")
causal_forest_results = list.files(path = "~/Desktop/Scenarios 11 & 12/Causal Forest",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# BKMR1 model
setwd("~/Desktop/Scenarios 11 & 12/BKMR1")
bkmr1_results = list.files(path = "~/Desktop/Scenarios 11 & 12/BKMR1",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time * 60 # convert to hours
  ) %>%
  distinct() %>% 
  select(-dataset)

# BART model
setwd("~/Desktop/Scenarios 11 & 12/BART")
bart_results = list.files(path = "~/Desktop/Scenarios 11 & 12/BART",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time * 60 # convert to hours
  ) %>%
  distinct() %>% 
  select(-dataset)
```

```{r}
# Load in true effects
true_effects = readRDS("~/Desktop/Columbia MS Biostatistics/Research/Valeri lab/Practicum/true_effects_new.RDS")
true_effects_mixture = readRDS("~/Desktop/Columbia MS Biostatistics/Research/Valeri lab/Practicum/true_effects_mixture_new.RDS")
```

```{r}
# Can also try to adjust true effects for metals 6-10 to 0.0000000001
true_effects_adj = true_effects[, 1:6] %>% 
  mutate(
    `6` = c(0.00000001, 0.00000001),
    `7` = c(0.00000001, 0.00000001),
    `8` = c(0.00000001, 0.00000001),
    `9` = c(0.00000001, 0.00000001),
    `10` = c(0.00000001, 0.00000001)
  )
```


# Performance Measurement

* Scenario 11: simple exposures, complex confounding, moderate collinearity
* Scenario 12: complex exposures, complex confounding, moderate collinearity

Note: besides confounders,exposure metals 1-5 are specified in the functional form for each scenario, while metals 6-10 are excluded. "Metal" 11 is the complete metal mixture.

```{r, cache = TRUE}
model_performance_dataset_level = function(df){
  
  rows = data.frame()
  
  df = df %>% 
    select(scenario:model_type)
  
  model_type = df$model_type[1]
  
  for (row_num in 1:nrow(df)){
    
    row = df[row_num, ]
    
    if (as.numeric(row$metal) %in% c(1:10)){
    
      true_effect = true_effects[as.numeric(row$scenario), as.numeric(row$metal) + 1]
    
    }
    
    if (as.numeric(row$metal) %in% c(11)){
    
      true_effect = true_effects_mixture[as.numeric(row$scenario), ][, 2]
    
    }
    
    row_truth = row %>%
      mutate(
        true_effect = as.numeric(true_effect)
      ) %>%
      mutate(
        point_bias = true_effect - point_estimate,
        relative_bias = point_bias / true_effect,
        standard_error = (true_effect - point_estimate)^2,
        includes = if_else(CI_lower <= true_effect & CI_upper >= true_effect,
                           1,
                           0),
        CI_length = CI_upper - CI_lower,
        sig_effect = case_when(
          CI_lower > 0 & CI_upper > 0 ~ 1,
          CI_lower < 0 & CI_upper < 0 ~ 1,
          CI_lower < 0 & CI_upper > 0 ~ 0
        )
      )
    
    rows = rbind(rows, row_truth)
    
  }
  
  return(rows)
  
}

model_performance_scenario_level = function(df){
  
  rows = data.frame()
  
  df = df %>% 
    select(scenario:model_type)
  
  model_type = df$model_type[1]
  
  for (row_num in 1:nrow(df)){
    
    row = df[row_num, ]
    
    if (as.numeric(row$metal) %in% c(1:10)){
    
      true_effect = true_effects[as.numeric(row$scenario), as.numeric(row$metal) + 1]
    
    }
    
    if (as.numeric(row$metal) %in% c(11)){
    
      true_effect = true_effects_mixture[as.numeric(row$scenario), ][, 2]
    
    }
    
    row_truth = row %>%
      mutate(
        true_effect = as.numeric(true_effect)
      ) %>%
      mutate(
        point_bias = abs(true_effect - point_estimate),
        relative_bias = point_bias / true_effect,
        standard_error = (true_effect - point_estimate)^2,
        includes = if_else(CI_lower <= true_effect & CI_upper >= true_effect,
                           1,
                           0),
        CI_length = CI_upper - CI_lower,
        sig_effect = case_when(
          CI_lower > 0 & CI_upper > 0 ~ 1,
          CI_lower < 0 & CI_upper < 0 ~ 1,
          CI_lower < 0 & CI_upper > 0 ~ 0
        )
      )
    
    rows = rbind(rows, row_truth)
    
  }
  
  performance_summary = rows %>% 
    group_by(scenario, metal) %>%
    summarize(
        RMSE = sqrt(mean(standard_error)),
        coverage = mean(includes),
        mean_sig_effect = mean(sig_effect),
        avg_time = mean(time)
      ) %>%
    mutate(
      power = dplyr::case_when(
        metal %in% c(1, 2, 3, 4, 5, 11) ~ mean_sig_effect,
        !(metal %in% c(1, 2, 3, 4, 5, 11)) ~ 1 - mean_sig_effect)
    ) %>% 
    select(scenario, metal, RMSE, coverage, power, avg_time)
  
  performance_summary$model_type = model_type
  
  return(performance_summary)
  
}
```

```{r, cache = TRUE, message = FALSE, warning = FALSE}
linear_model_performance_dataset_level = model_performance_dataset_level(linear_results)
linear_model_performance_scenario_level = model_performance_scenario_level(linear_results)

elastic_net_model_performance_dataset_level = model_performance_dataset_level(elastic_net_results)
elastic_net_model_performance_scenario_level = model_performance_scenario_level(elastic_net_results)

mars_model_performance_dataset_level = model_performance_dataset_level(mars_results)
mars_model_performance_scenario_level = model_performance_scenario_level(mars_results)

gam1_model_performance_dataset_level = model_performance_dataset_level(gam1_results)
gam1_model_performance_scenario_level = model_performance_scenario_level(gam1_results)

qgcomp_model_performance_dataset_level = model_performance_dataset_level(qgcomp_results)
qgcomp_model_performance_scenario_level = model_performance_scenario_level(qgcomp_results)

causal_forest_model_performance_dataset_level = model_performance_dataset_level(causal_forest_results)
causal_forest_model_performance_scenario_level = model_performance_scenario_level(causal_forest_results)

bkmr1_model_performance_dataset_level = model_performance_dataset_level(bkmr1_results)
bkmr1_model_performance_scenario_level = model_performance_scenario_level(bkmr1_results)

bart_model_performance_dataset_level = model_performance_dataset_level(bart_results)
bart_model_performance_scenario_level = model_performance_scenario_level(bart_results)


dataset_level_performance = rbind(linear_model_performance_dataset_level,
                                  elastic_net_model_performance_dataset_level,
                                  mars_model_performance_dataset_level,
                                  gam1_model_performance_dataset_level,
                                  qgcomp_model_performance_dataset_level,
                                  causal_forest_model_performance_dataset_level,
                                  bkmr1_model_performance_dataset_level,
                                  bart_model_performance_dataset_level)

scenario_level_performance = rbind(linear_model_performance_scenario_level,
                                   elastic_net_model_performance_scenario_level,
                                   mars_model_performance_scenario_level,
                                   gam1_model_performance_scenario_level,
                                   qgcomp_model_performance_scenario_level,
                                   causal_forest_model_performance_scenario_level,
                                   bkmr1_model_performance_scenario_level,
                                   bart_model_performance_scenario_level)
```

## Relative Bias

### Data Visualizations

```{r}
# Relative bias distributions

# Individual metals
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  ggplot(aes(x = model_type, y = relative_bias)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Distribution of Relative Bias by Scenario & Model",
       subtitle = "For Exposures in Functional Form (Metals 1-5)")

# Mixture
dataset_level_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = model_type, y = relative_bias)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Distribution of Relative Bias by Scenario & Model",
       subtitle = "For Full Metal Mixture")
```

```{r}
# Relative bias medians, grouped by metal

# Individual metals
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    median_relative_bias = median(relative_bias)
  ) %>% 
  ggplot(aes(x = model_type, y = median_relative_bias)) + 
  geom_point() + 
  facet_grid(metal ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Median Relative Bias by Scenario & Model, Grouped by Metal",
       subtitle = "For Exposures in Functional Form (Metals 1-5)")

# Mixture
dataset_level_performance %>% 
  filter(metal == 11) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    median_relative_bias = median(relative_bias)
  ) %>% 
  ggplot(aes(x = model_type, y = median_relative_bias)) + 
  geom_point() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Median Relative Bias by Scenario & Model",
       subtitle = "For Full Metal Mixture")
```

```{r}
# Table format: minima (scenario 11)
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 11) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ) %>% 
  filter(scenario == 11) %>% 
  group_by(metal) %>% 
  summarize(
    min_abs_median_relative_bias = min(abs(abs_median_relative_bias))
  ) %>% 
  inner_join(
    dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 11) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ),
  by = join_by(min_abs_median_relative_bias == abs_median_relative_bias, metal == metal),
  multiple = "all"
  )

# Table format: maxima (scenario 11)
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 11) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ) %>% 
  filter(scenario == 11) %>% 
  group_by(metal) %>% 
  summarize(
    max_abs_median_relative_bias = max(abs(abs_median_relative_bias))
  ) %>% 
  inner_join(
    dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5), scenario == 11) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ),
  by = join_by(max_abs_median_relative_bias == abs_median_relative_bias, metal == metal),
  multiple = "all"
  )

# Table format: minima (scenario 12)
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 12) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ) %>% 
  filter(scenario == 12) %>% 
  group_by(metal) %>% 
  summarize(
    min_abs_median_relative_bias = min(abs(abs_median_relative_bias))
  ) %>% 
  inner_join(
    dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 12) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ),
  by = join_by(min_abs_median_relative_bias == abs_median_relative_bias, metal == metal),
  multiple = "all"
  )

# Table format: maxima (scenario 12)
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5,11), scenario == 12) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ) %>% 
  filter(scenario == 12) %>% 
  group_by(metal) %>% 
  summarize(
    max_abs_median_relative_bias = max(abs(abs_median_relative_bias))
  ) %>% 
  inner_join(
    dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5), scenario == 12) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    abs_median_relative_bias = abs(median(relative_bias))
  ),
  by = join_by(max_abs_median_relative_bias == abs_median_relative_bias, metal == metal),
  multiple = "all"
  )
```

```{r}
# Relative bias medians, not grouped by metal

# Individual metals
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  group_by(scenario, model_type) %>% 
  summarize(
    median_relative_bias = median(relative_bias)
  ) %>% 
  ggplot(aes(x = scenario, y = median_relative_bias, color = model_type)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Median Relative Bias by Scenario & Model, Not Grouped By Metal",
       subtitle = "For Exposures in Functional Form (Metals 1-5)")

# Mixture
# Is same as earlier, because only one metal
# dataset_level_performance %>% 
#   filter(metal == 11) %>% 
#   group_by(scenario, model_type) %>% 
#   summarize(
#     median_relative_bias = median(relative_bias)
#   ) %>% 
#   ggplot(aes(x = model_type, y = median_relative_bias)) + 
#   geom_point() + 
#   facet_grid(. ~ scenario) + 
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# Check that median relative bias is generally worse for scenario 12 than for scenario 11
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    median_relative_bias = median(relative_bias)
  ) %>% 
  ggplot(aes(x = model_type, y = median_relative_bias, color = scenario)) + 
geom_point() + 
  facet_grid(. ~ metal)  +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Median Relative Bias by Model and Metal, Colored by Scenario",
       subtitle = "For Exposures in Functional Form (Metals 1-5)")
```

### Observations

* Generally, relative bias is in a tighter range for MARS, GAM, and causal forest compared to linear, elastic net, or quantile g-computation (qgcomp) -- and across model types, is in a tighter range for scenario 12 (complex exposures) than for scenario 11 (simple exposures)
* For scenario 11, GAM model almost universally has lowest minimum absolute value of median relative bias for each metal; qgcomp and MARS model generally have highest, tending to perform worse than even linear/elastic net
* For scenario 12, linear, causal forest, and qgcomp models have lowest minimum absolute value of median relative bias for each metal; MARS model is almost universally worst, with highest max absolute value of median relative bias for each metal (except for metal 1, where qgcomp is worst)
* When not grouping by metal, GAM does best for scenario 11 and scenario 12, while MARS does worst for scenario 11 and scenario 12
* As expected, median relative bias is generally (though not completely consistently) better for each unique metal/model type in scenario 11 compared to scenario 12
* Causal Forest performs perhaps most similarly in scenario 11 vs. scenario 12; still relatively consistent despite complex confounding structure

## RMSE

### Data Visualizations

```{r}
# RMSE

# Individual metals
scenario_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  ggplot(aes(x = metal, y = RMSE, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "RMSE by Scenario & Model",
       subtitle = "For Exposures in Functional Form (Metals 1 & 5)")

# Individual metals, alternative viz
scenario_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  ggplot(aes(x = scenario, y = RMSE, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ metal) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "RMSE by Scenario & Model",
       subtitle = "For Exposures in Functional Form (Metals 1 & 5)")

# Mixture
scenario_level_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = scenario, y = RMSE, color = model_type)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "RMSE by Scenario & Model",
       subtitle = "For Full Metal Mixture")
```

### Observations

* For both scenarios, RMSE generally minimized by causal forest (and sometimes GAM) but maximized by qgcomp (and sometimes linear model)
* For full metal mixtures, RMSE is minimized by GAM and MARS for scenario 11, and causal forest for scenario 12; for scenario 11, maximized by linear, but for scenario 12, maximized by qgcomp

## Other Measures

```{r}
# Variance
dataset_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  ggplot(aes(x = model_type, y = variance)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Distribution of Variance by Scenario & Model",
       subtitle = "For Exposures in Functional Form (Metals 1 & 5)")

dataset_level_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = model_type, y = variance)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Distribution of Variance by Scenario & Model",
       subtitle = "For Full Metal Mixture")
```

```{r}
# Coverage

# Individual metals
scenario_level_performance %>% 
  filter(metal %in% c(1,2,3,4,5)) %>% 
  ggplot(aes(x = metal, y = coverage, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Coverage by Scenario & Model",
       subtitle = "For Exposures in Functional Form (Metals 1 & 5)")

# Mixture
scenario_level_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = metal, y = coverage, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Coverage by Scenario & Model",
       subtitle = "For Full Metal Mixture")
```

# Appendix


```{r}
# Grid of metrics (rows) x scenarios (columns)
# all_performance %>% 
#   filter(metal %in% c(1, 5, 11)) %>% 
#   pivot_longer(cols = mean_point_estimate:avg_time,
#                names_to = "metric") %>% 
#   filter(metric %in% c("relative_bias", "coverage", "power", "RMSE")) %>% 
#   ggplot(aes(x = metal, y = value, color = model_type)) + 
#   geom_point() + 
#   facet_grid(scenario ~ metric)
```

```{r}
# With adjusted true effects for metals 6-10
model_performance_dataset_level_adj = function(df){
  
  rows = data.frame()
  
  df = df %>% 
    select(scenario:model_type)
  
  model_type = df$model_type[1]
  
  for (row_num in 1:nrow(df)){
    
    row = df[row_num, ]
    
    if (as.numeric(row$metal) %in% c(1:10)){
    
      true_effect = true_effects_adj[as.numeric(row$scenario), as.numeric(row$metal) + 1]
    
    }
    
    if (as.numeric(row$metal) %in% c(11)){
    
      true_effect = true_effects_mixture[as.numeric(row$scenario), ][, 2]
    
    }
    
    row_truth = row %>%
      mutate(
        true_effect = as.numeric(true_effect)
      ) %>%
      mutate(
        point_bias = true_effect - point_estimate,
        relative_bias = point_bias / true_effect,
        standard_error = (true_effect - point_estimate)^2,
        includes = if_else(CI_lower <= true_effect & CI_upper >= true_effect,
                           1,
                           0),
        CI_length = CI_upper - CI_lower,
        sig_effect = case_when(
          CI_lower > 0 & CI_upper > 0 ~ 1,
          CI_lower < 0 & CI_upper < 0 ~ 1,
          CI_lower < 0 & CI_upper > 0 ~ 0
        )
      )
    
    rows = rbind(rows, row_truth)
    
  }
  
  return(rows)
  
}

model_performance_scenario_level_adj = function(df){
  
  rows = data.frame()
  
  df = df %>% 
    select(scenario:model_type)
  
  model_type = df$model_type[1]
  
  for (row_num in 1:nrow(df)){
    
    row = df[row_num, ]
    
    if (as.numeric(row$metal) %in% c(1:10)){
    
      true_effect = true_effects_adj[as.numeric(row$scenario), as.numeric(row$metal) + 1]
    
    }
    
    if (as.numeric(row$metal) %in% c(11)){
    
      true_effect = true_effects_mixture[as.numeric(row$scenario), ][, 2]
    
    }
    
    row_truth = row %>%
      mutate(
        true_effect = as.numeric(true_effect)
      ) %>%
      mutate(
        point_bias = abs(true_effect - point_estimate),
        relative_bias = point_bias / true_effect,
        standard_error = (true_effect - point_estimate)^2,
        includes = if_else(CI_lower <= true_effect & CI_upper >= true_effect,
                           1,
                           0),
        CI_length = CI_upper - CI_lower,
        sig_effect = case_when(
          CI_lower > 0 & CI_upper > 0 ~ 1,
          CI_lower < 0 & CI_upper < 0 ~ 1,
          CI_lower < 0 & CI_upper > 0 ~ 0
        )
      )
    
    rows = rbind(rows, row_truth)
    
  }
  
  performance_summary = rows %>% 
    group_by(scenario, metal) %>%
    summarize(
        RMSE = sqrt(mean(standard_error)),
        coverage = mean(includes),
        mean_sig_effect = mean(sig_effect),
        avg_time = mean(time)
      ) %>%
    mutate(
      power = dplyr::case_when(
        metal %in% c(1, 2, 3, 4, 5, 11) ~ mean_sig_effect,
        !(metal %in% c(1, 2, 3, 4, 5, 11)) ~ 1 - mean_sig_effect)
    ) %>% 
    select(scenario, metal, RMSE, coverage, power, avg_time)
  
  performance_summary$model_type = model_type
  
  return(performance_summary)
  
}
```

```{r, cache = TRUE, message = FALSE, warning = FALSE}
linear_model_performance_dataset_level_adj = model_performance_dataset_level_adj(linear_results)
linear_model_performance_scenario_level_adj = model_performance_scenario_level_adj(linear_results)

elastic_net_model_performance_dataset_level_adj = model_performance_dataset_level_adj(elastic_net_results)
elastic_net_model_performance_scenario_level_adj = model_performance_scenario_level_adj(elastic_net_results)

mars_model_performance_dataset_level_adj = model_performance_dataset_level_adj(mars_results)
mars_model_performance_scenario_level_adj = model_performance_scenario_level_adj(mars_results)

gam1_model_performance_dataset_level_adj = model_performance_dataset_level_adj(gam1_results)
gam1_model_performance_scenario_level_adj = model_performance_scenario_level_adj(gam1_results)

qgcomp_model_performance_dataset_level_adj = model_performance_dataset_level_adj(qgcomp_results)
qgcomp_model_performance_scenario_level_adj = model_performance_scenario_level_adj(qgcomp_results)

dataset_level_performance_adj = rbind(linear_model_performance_dataset_level_adj,
                                  elastic_net_model_performance_dataset_level_adj,
                                  mars_model_performance_dataset_level_adj,
                                  gam1_model_performance_dataset_level_adj,
                                  qgcomp_model_performance_dataset_level_adj)

scenario_level_performance_adj = rbind(linear_model_performance_scenario_level_adj,
                                   elastic_net_model_performance_scenario_level_adj,
                                   mars_model_performance_scenario_level_adj,
                                   gam1_model_performance_scenario_level_adj,
                                   qgcomp_model_performance_scenario_level_adj)
```

```{r}
# Relative bias distributions

# Individual metals
dataset_level_performance_adj %>% 
  filter(metal %in% c(1,2,3,4,5,6,7,8,9,10)) %>% 
  ggplot(aes(x = model_type, y = relative_bias)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
  labs(title = "Distribution of Relative Bias by Scenario & Model",
       subtitle = "For All Metals 1-10")

# Individual metals
dataset_level_performance_adj %>% 
  filter(metal %in% c(1,2,3,4,5,6,7,8,9,10)) %>% 
  group_by(scenario, metal, model_type) %>% 
  summarize(
    median_relative_bias = median(relative_bias)
  ) %>% 
  ggplot(aes(x = model_type, y = median_relative_bias)) + 
  geom_point() + 
  facet_grid(metal ~ scenario) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Median Relative Bias by Scenario & Model, Grouped by Metal",
       subtitle = "For All Metals 1-10")
```

