---
title: "Model Performance Results"
author: 'Zachary Katz (UNI: zak2132)'
date: "2023-02-24"
output: html_document
---

# Data Import & Wrangling

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r, cache = TRUE, message = FALSE, warning = FALSE}
# Import model results

# Linear model
setwd("~/Desktop/Linear/Results/")
linear_results = list.files(path = "~/Desktop/Linear/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time / 60 # time in minutes
  ) %>% 
  distinct() %>% 
  select(-dataset)

# Elastic net model
setwd("~/Desktop/Elastic Net/Results/")
elastic_net_results = list.files(path = "~/Desktop/Elastic Net/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# MARS model
setwd("~/Desktop/MARS/Results/")
mars_results = list.files(path = "~/Desktop/MARS/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# GAM1 model
setwd("~/Desktop/GAM1/Results/")
gam1_results = list.files(path = "~/Desktop/GAM1/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal),
    time = time * 60 # convert to hours
  ) %>% 
  distinct() %>% 
  select(-dataset)

# Quantile G-Computation model
setwd("~/Desktop/Quantile G-Computation/Results/")
qgcomp_results = list.files(path = "~/Desktop/Quantile G-Computation/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)

# Causal Forest model
setwd("~/Desktop/Causal Forest/Results/")
causal_forest_results = list.files(path = "~/Desktop/Causal Forest/Results/",
                            pattern = "*.csv") %>% 
  map_df(~read_csv(.)) %>% 
  as.data.frame() %>% 
  mutate(
    scenario = as.factor(scenario),
    metal = as.factor(metal)
  ) %>% # time already in minutes
  distinct() %>% 
  select(-dataset)
```

```{r}
# Load in true effects
true_effects = readRDS("~/Desktop/Columbia MS Biostatistics/Research/Valeri lab/Practicum/true_effects.RDS")
true_effects_mixture = readRDS("~/Desktop/Columbia MS Biostatistics/Research/Valeri lab/Practicum/true_effects_mixture.RDS")
```

```{r, cache = TRUE}
model_performance = function(df){
  
  rows = data.frame()
  
  df = df %>% 
    select(scenario:model_type)
  
  model_type = df$model_type[1]
  
  for (row_num in 1:nrow(df)){
    
    row = df[row_num, ]
    
    if (as.numeric(row$metal) %in% c(1:10)){
    
      true_effect = true_effects[as.numeric(row$scenario), as.numeric(row$metal) + 1]
    
    }
    
    if (as.numeric(row$metal) %in% c(11)){
    
      true_effect = true_effects_mixture[as.numeric(row$scenario), ][, 2]
    
    }
    
    row_truth = row %>%
      mutate(
        true_effect = as.numeric(true_effect)
      ) %>%
      mutate(
        point_bias = abs(true_effect - point_estimate),
        standard_error = (true_effect - point_estimate)^2,
        includes = if_else(CI_lower <= true_effect & CI_upper >= true_effect,
                           1,
                           0),
        CI_length = CI_upper - CI_lower,
        sig_effect = case_when(
          CI_lower > 0 & CI_upper > 0 ~ 1,
          CI_lower < 0 & CI_upper < 0 ~ 1,
          CI_lower < 0 & CI_upper > 0 ~ 0
        )
      )
    
    rows = rbind(rows, row_truth)
    
  }
  
  performance_summary = rows %>% 
    group_by(scenario, metal) %>%
    summarize(
        mean_point_estimate = mean(point_estimate),
        true_effect = mean(true_effect),
        bias = mean(abs(point_bias)),
        relative_bias = bias / true_effect,
        relative_perc_diff = 2 * (bias - true_effect) / (abs(bias) + abs(true_effect)),
        variance_point_estimate = var(point_estimate),
        RMSE = sqrt(mean(standard_error)),
        coverage = mean(includes),
        mean_sig_effect = mean(sig_effect),
        avg_time = mean(time)
      ) %>%
    mutate(
      power = dplyr::case_when(
        metal %in% c(1, 5, 11) ~ mean_sig_effect,
        !(metal %in% c(1, 5, 11)) ~ 1 - mean_sig_effect)
    ) %>% 
    select(scenario, metal, mean_point_estimate, bias, relative_bias, relative_perc_diff, variance_point_estimate, RMSE, coverage, power, avg_time)
  
  performance_summary$model_type = model_type
  
  return(performance_summary)
  
}
```

```{r, cache = TRUE}
# Check performance
linear_performance = model_performance(linear_results)
elastic_net_performance = model_performance(elastic_net_results)
mars_performance = model_performance(mars_results)
gam1_performance = model_performance(gam1_results)
qgcomp_performance = model_performance(qgcomp_results)

all_performance = rbind(linear_performance, elastic_net_performance, mars_performance, gam1_performance, qgcomp_performance)
```

# Model Performance Viz

* Scenario 1: baseline (simple exposures, simple confounding)
* Scenario 2: complex exposures (nonlinear / interactions), simple confounding
* Scenario 3: complex exposures (nonlinear / interactions) + multicollinearity, simple confounding
* Scenario 4: complex exposures (trigonometric), simple confounding
* Scenario 5: complex exposures (trigonometric) + multicollinearity, simple confounding
* Scenario 6: simple exposures, complex confounding
* Scenario 7: complex exposures (nonlinear / interactions), complex confounding
* Scenario 8: complex exposures (trigonometric), complex confounding
* Scenario 9: complex exposures (nonlinear / interactions) + multicollinearity, complex confounding
* Scenario 10: complex exposures (trigonometric) + multicollinearity, complex confounding

Note: besides confounders, only exposure metals 1 and 5 are specified in the functional form for each scenario. "Metal" 11 is the complete metal mixture.

## Relative Bias

```{r}
all_performance %>% 
  filter(metal %in% c(1,5)) %>% 
  ggplot(aes(x = scenario, y = relative_bias, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ metal)
```

```{r}
# Explorations of relative bias by scenario, all metals and models
all_performance %>% 
  ggplot(aes(x = model_type, y = relative_bias)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

# Explorations of relative bias by scenario, only metals 1 and 5 (all models)
all_performance %>% 
  filter(metal %in% c(1, 5)) %>% 
  ggplot(aes(x = model_type, y = relative_bias)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Observations:
* In general, lowest bias seen for scenarios 4, 5, and 6; moderate bias seen for scenarios 1, 8, and 10; higher bias seen for scenarios 2, 3, 7, and 9
* Quantile G-Computation seems to have much higher bias in all scenarios
* Relative bias lower for elastic net and linear models in most scenarios

```{r}
# Explorations of relative bias by scenario, metal mixture only
all_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = scenario, y = relative_bias, color = model_type)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Observations:
* Again, quantile g-computation has high bias across most scenarios
* Lower bias in scenarios 4, 5, 6, 8, and 10, but higher bias in scenarios 1, 2, 3, 7, and 9
* Linear and elastic net models perform better than expected in many cases, whereas GAM in particular tends to perform worse

## RMSE

```{r}
all_performance %>% 
  filter(metal %in% c(1,5)) %>% 
  ggplot(aes(x = scenario, y = RMSE, color = model_type)) + 
  geom_point() + 
  facet_grid(. ~ metal)
```

```{r}
# Explorations of relative bias by scenario, all metals and models
all_performance %>% 
  ggplot(aes(x = model_type, y = RMSE)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

# Explorations of relative bias by scenario, only metals 1 and 5 (all models)
all_performance %>% 
  filter(metal %in% c(1, 5)) %>% 
  ggplot(aes(x = model_type, y = RMSE)) + 
  geom_boxplot() + 
  facet_grid(. ~ scenario) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Observations:
* In general, lowest RMSE seen for scenarios 1, 4, 5, and 6; moderate RMSE seen for scenarios 8 and 10; higher RMSE seen for scenarios 2, 3, 7, and 9
* Quantile G-Computation seems to have much higher RMSE in all scenarios
* RMSE slightly lower for elastic net and linear models in most scenarios

```{r}
# Explorations of relative bias by scenario, metal mixture only
all_performance %>% 
  filter(metal == 11) %>% 
  ggplot(aes(x = scenario, y = RMSE, color = model_type)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Observations:
* Again, quantile g-computation has high RMSE across most scenarios
* Lower RMSE in scenarios 1, 4, 5, 6, 8, and 10, but higher RMSE in scenarios 2, 3, 7, and 9
* Linear and elastic net models perform better than expected in many cases, whereas GAM in particular tends to perform worse

# Takeaways

## Descriptive

* Which scenarios are supposed to be less challenging for the models to estimate? *1, 2, and 4*
* Which scenarios are in actuality less challenging for the models to estimate (i.e. seem to have lowest relative bias and RMSE)? *4, 5, 6, and perhaps 1*
* Which scenarios are supposed to be more challenging for the models to estimate? *3, 5, 9, and 10*
* Which scenarios are in actuality more challenging for the models to estimate (i.e. seem to have highest relative bias and RMSE)? *2, 3, 7, and 9*
* Which scenarios are supposed to be moderately challenging for the models to estimate? *6, 7, and 8*
* Which scenarios are supposed to be relatively similar to each other? *2 and 4; 3 and 5; 7 and 8; 9 and 10*

* Scenarios we thought would be easy that actually are easy: *1 and 4*
* Scenarios we thought would be easy that actually are challenging: *2*
* Scenarios we thought would be challenging that actually are challenging: *3 and 9*
* Scenarios we thought would be challenging that actually are easy: *None (potentially 6)*
* Scenarios that perform similarly to each other we assumed would perform similarly to each other: *None*
* Scenarios that perform similarly to each other we did not assume would perform similarly to each other: *2 and 3; 4 and 5; 7 and 9; 8 and 10*

## Insights

* Multicollinearity between the exposures does not seem to matter re: model performance (perhaps because limited variable selection implemented?)
* Functional forms specified nonlinearly (polynomial) and with interaction terms are more difficult than those specified trigonometrically 
* Complex confounding seems to add some -- but only a little bit -- of challenge for model estimation / performance
* Linear and elastic net models seem to overperform in most scenarios, indicating that our functional forms may be too "easy" (specify more exposures?)

## Recommendations

* Definitely drop: scenarios 4, 5, 8, and 10
* Consider dropping: scenarios 3 and 9 [but potentially keep because still relatively challenging]
* For scenarios 6 and 7, find a way to introduce more complex confounding?
* Introduce more complex functional forms, with more exposures?

# Work in Progress

```{r}
# Grid of metrics (rows) x scenarios (columns)
all_performance %>% 
  filter(metal %in% c(1, 5, 11)) %>% 
  pivot_longer(cols = mean_point_estimate:avg_time,
               names_to = "metric") %>% 
  filter(metric %in% c("relative_bias", "coverage", "power", "RMSE")) %>% 
  ggplot(aes(x = metal, y = value, color = model_type)) + 
  geom_point() + 
  facet_grid(scenario ~ metric)
```

